---
output:
  word_document:
    fig_caption: true
    fig_height: 10
    fig_width: 10
    reference_docx: model/reportTemplate.docx
    toc: true
    keep_md: true
params:
  report_title: ""
---

```{r introduction, include = FALSE}

# INTRODUCTION ################################################################

# This markdown documents and integrated scripts analyse biological
# age readings.
# The output is a .docx template that includes
# the results of the analysis and should be used as a standard for
# reporting of age reading comparisons.

```

```{r chunk_setup, include=FALSE}

# CHUNK SETUPS #################################################################

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, 
                      message=FALSE, results = 'asis', dpi=400)

```

```{r pander_settings, include = FALSE}

# PANDER OPTIONS ##############################################################

panderOptions('table.split.table', Inf)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('table.alignment.default', "center")

```

---
title: `r params$report_title`
---

# Executive summary

# Terms of reference

# Agenda and participant list

The agenda can be found in Annex 1 and the list of participants in Annex 2.


# Introduction

This part should include a background to the species, the workshop/exchange 
and what to expect to read about in the report.


# Methods

This report contains statistical analyses and comparisons of age readings 
in the form of tables and graphical plots.

First, an overview of participating age readers and the samples are presented.

Before each table or plot there is a short explanation of it. This text is 
thought as a help to understand the tables/plot and can just be deleted in 
the final output report. The document can be edited just like any other 
.docx file. New text can be added, additional pictures can be included and 
the tables edited. If some tables which are presently in the annexes need to 
be moved to the body of the report this is also possible. Only the plots 
cannot be changed.

In the first part of analysis are presented the tables and plots from the 
Guus Eltink Excel sheet 'Age Reading Comparisons' **(Eltink, A.T.G.W. 2000)**. 
The order and numbering of tables and plots are the same as in the excel sheet. 
Tables 6.1 - 6.4 from the 'Age Reading Comparisons' sheet are not outputted 
since these are merely used to do calculations for the other tables.


**Pecentage Agreement**

In here will go some text and an equation.


**Co-efficient of Variation (CV)**

The table presents the cv per modal age and reader. The cv's are calculated
as the ratio between the standard deviation (σ) and mean value (μ) per 
reader and modal age:

$$CV = { \frac{ {\sigma}} {\mu} } \cdot {100 \%} $$

To the table is also added the CV of all readers combined per modal age and
a weighted mean of the CV per reader. Finally a rank value is added per 
reader, where the reader with the lowest weighted mean is assigned with 
a rank and so forth (in the situation of ties between two weighted means 
will every tied element be assigned to the lowest rank. This is the procedure
for all ties methods when assigning ranks).


**Average Percentage Error (APE)**

APE was calculated based on the method outlined by Beamish & Fournier (1981).
This method is not independent of fish age and thus provides a better estimate
of precision. As the calculations of both CV and APE pose problems if the mean
age is close to 0, all observations for which modal age was 0 were omitted
from the CV and APE calculations.

The average percentage error is calculated per image as:



$$APE = { \frac{ {100 \%}} {n} \sum_{i=1}^n |\frac{a_i-\bar{a}}{\bar{a}}| } $$
where $a_i$ is the age reading of reader $i$ and ${\bar{a}}$ is the mean
of all readings from 1 to $n$.


**Age error matricx (AEM)**

Age error matrices (AEM) were produced following procedures outlined 
by WKSABCAL (2014) where the matrix shows the proportion of each modal
age mis-aged as other ages. The sum of each row is 1, which equals 100%. 
The age data was analysed twice, the first time all readers were included
and the second time only the “advanced” readers were included. If a reader
is “advanced” then they are considered well trained and they provide ages
for stock assessment or similar purposes.  When the AEM is compiled for
assessment purposes it uses only those readers who provide age data for
the stock assessment in that specific area.


**Otolith Growth Analysis**

SmartDots provides a measure of distance between the annotations made by
the readers and thus provides a measure of growth increment width. 
This data is used to establish growth curves for each fish and for each reader.



# Analysis of age calibration exercise (ToR?)


## Overview of samples and readers


\br

```{r sample_overview}

# Table caption
set.caption('**Table X:** Overview of samples used for the xxx exchange.')

# Output table
pander(style_table0(sample_dat_ov), style = "simple")

```

\br

```{r participants_overview}

# PARTICIPATANTS OVERVIEW #####################################################

# Table caption
set.caption('**Table X:** Reader overview.')

# Output table
pander(style_table0(part_tab[,c("Reader code", "Expertise")]), missing = "-")

```


## Results 

### All readers

**All samples included** 

Those writing the report put TEXT here describing the results.

<!-- PA, CV and APE text --> 

The average percentage agreement based on modal ages accross all annotations 
is `r round(sum_stat[1],1)`%, with an average CV of `r round(sum_stat[2],1)`%.
The APE is `r round(sum_stat[3],1)`%.

```{r cv_table}

# CV TABLE - All readers ######################################################

# Table caption
set.caption('**Table X:** Coefficient of Variation (CV) table presents the CV
             per modal age and reader, the CV of all readers combined per modal 
             age and a weighted mean of the CV per reader. 
             A rank is also assigned to each reader.')

# Output table
pander(style_table2(cv_tab), missing = "-")

```

<!-- PA text -->
The percentage agreement per reader per modal age tells how large part of the 
readings that are equal to the modal age. The weighted mean including at the 
bottom of the table is weighted according to number of age readings. 
A rank is also assigned to each reader.

```{r percentage_agreement}

# PERCENTAGE AGREEMENT TABLE - All readers ####################################

# Table caption
set.caption('**Table X:** Percentage agreement (PA) table represents the PA per
             modal age and reader, the PA of all readers combined per modal
             age and a weighted mean of the PA per reader.
             A rank is also assgned to each reader.')

# Output table
pander(style_table2(pa_tab[,c(1:ncol(pa_tab))]), missing="-")

```

<!-- Relative bias text -->
The relative bias is the difference between the mean age (per modal age per 
reader) and modal age. As for the previous tables, a combined bias for all 
readers and weighted means are calculated and finally a rank is assigned 
to each reader.

```{r rb}

# RELATIVE BIAS TABLE - All readers ###########################################

# Table caption
set.caption('**Table X:** Relative bias table represents the relative bias per 
             modal age per reader, the relative bias of all readers combined
             per modal age and a weighted mean of the relative bias per reader.
             A rank is also assigned to each reader.')

# Output table
pander(style_table2(rb_tab), missing = "-")

```

```{r bias_plots_all, fig.width = 5, fig.height = 4, fig.cap = cap_in}

# BIAS PLOTS - All readers ####################################################

# Figure Caption
cap_in <- '**Figure X:**: Age bias plot for all readers. Mean age 
           recorded +/- 2 stdev of each reader and all readers combined are 
           plotted against modal age. The estimated man age corresponds to 
           modal age, if the estimated mean age is on the 1:1 equilibrium 
           line (solid line). Relative bias is the age difference between 
           estimated mean age and modal age.'

# Output figure 
plot_bias_all(ad_long, max_age, max_modal)

```

<!-- Inter reader bias text -->
For each pair that is being compared, the differences between the readings
per image are found and the frequency of each occurring difference is obtained.
A rank value is calculated for the positive and the negative differences 
(R+ and R- in the Guus Eltink sheet). The value with the smallest rank is then
used to calculate a z-value that determines the level of bias (not clear from
Guus Eltink sheet how the equations are defined..).

```{r bias_table}

# INTER READER BIAS TEST - All readers ########################################

# Table caption
set.caption('**Table X:** Inter reader bias test. The Inter-reader bias test
             gives probability of bias between readers and with modal age. 
             - = no sign of bias (p>0.05), * = possibility of bias 
             (0.01<p<0.05), * * = certainty of bias (p<0.01) ')

# Output table
pander(style_table3(bias_tab), missing = ".", style = "simple")

```

```{r growth_analysis, fig.width = 8, fig.height = 6, fig.cap = cap_in}

# GROWTH ANALYSIS - All readers ###############################################

# Figure caption
cap_in <- '**Table X:** Plot of average distance from the centre to the winter
           rings for all readers. The boxes represent the mean, upper and lower
           box boundaries of the interquartile range, whiskers represent the
           minimum and maximum values and the dots represent the outliers.'

# Output figure
plot_growth(dist, compl_sample, part_tab2, "All")

```



**Results by month** 

```{r num_month}

# NUMBER OF AGE READINGS PER MONTH - All readers ##################################

# Table caption
set.caption('**Table X:** Number of age readings per month.')

# Output table
pander(style_table1(num_mo_comp), missing = "-")

```

```{r cv_month}

# CV PER MONTH - All readers ##################################################

# Table caption
set.caption('**Table X:** CV per month.')

# Output table
pander(style_table2(cv_mo_tab), missing = "-")

```

```{r pa_month}

# PA PER MONTH - All readers ##################################################

# Table caption
set.caption('**Table X:** Percentage agreement per month.')

# Output table
pander(style_table2(pa_mo_tab), missing = "-")

```

```{r rb_month}

# RELATIVE BIAS PER MONTH - All readers #######################################

# Table caption
set.caption('**Table X:** Relative bias per month.')

# Output table
pander(style_table2(rb_mo_tab), missing = "-")

```

### Advanced readers

**All samples included** 

```{r cv_ex}

# CV TABLE - Advanced readers #################################################

# Table caption
set.caption('**Table X:** Coefficient of Variation (CV) table presents the
             CV per modal age and advanced reader, the CV of all advanced
             readers combined per modal age and a weighted mean of the CV
             per reader. A rank is also assigned to each reader.')

# Output table
pander(style_table1(cv_tab_ex), missing = "-")

```

```{r percentage_agreement_ex}

# PERCENTAGE AGREEMENT TABLE - Advanced readers ###############################

# Table caption
set.caption('**Table X:** Percentage agreement (PA) table represents the PA per
             modal age and reader, advanced the PA of all advanced readers
             combined per modal age and a weighted mean of the PA per reader. 
             A rank is also assgned to each reader.')

# Output table
pander(style_table2(pa_tab_ex), missing = "-")

```

```{r rb_ex,results='asis'}

# RELATIVE BIAS TABLE - Advanced readers ######################################

# Table caption
set.caption('**Table X:** Relative bias table represents the relative bias per
             modal age and advanced reader, the relative bias of all
             advanced readers combined per modal age and a weighted mean of
             the relative bias per reader. A rank is also assigned to 
             each reader.')

# Output table 
pander(style_table2(rb_tab_ex), missing = "-")

```

```{r bias_plots_exp, fig.width = 5, fig.height = 4, fig.cap = cap_in}

# BIAS PLOT - Advanced readers ################################################

# Table caption
cap_in <- '**Figure X:** Age bias plot for advanced readers.'

# Output table
plot_bias_all(ad_long_ex, max_age, max_modal)

```

\br
```{r growth_analysis_exp, fig.width = 8, fig.height = 6, fig.cap = cap_in}

# GROWTH ANALYSIS - Advanced readers ##########################################

# Table caption
cap_in <- '**Figure X:** Plot of average distacne from the centre to the winter
           rings for advanced readers. The boxes represent the mean, upper and
           lower box boundaries of the interquartile range, whiskers represent
           the minimum and maximum values and the dots represent the outliers.'

# Output table
plot_growth(dist, compl_sample, part_tab2, "Expert")

```


**Results by month**

```{r num_month_ex}

# NUMBER OF AGE READINGS PER MONTH - Advanced readers #########################

# Table caption
set.caption('**Table X:** Number of age readings per month for 
             advanced readers.')

# Output table
pander(style_table1(num_mo_comp_ex), missing = "-")

```

```{r cv_month_ex}

# CV PER MONTH - Advanced readers #############################################

# Table caption
set.caption('**Table X:** CV per month.')

# Output table
pander(style_table2(cv_mo_tab_ex), missing = "-")

```

```{r pa_month_ex}

# PA PER MONTH - Advanced readers #############################################

# Table caption
set.caption('**Table X:** Percentage agreement per month.')

# Output table
pander(style_table2(pa_mo_tab_ex), missing = "-")

```

```{r rb_month_ex}

# RELATIVE BIAS PER MONTH - Advanced readers ##################################

# Table caption
set.caption('**Table X:** Relative bias per month.')

# Output table
pander(style_table2(rb_mo_tab_ex), missing = "-")

```


## Discussion

## Conclusion


<!------------------------------ OTHER --------------------------------------->

# Other ToRs

# References


<!------------------------------ ANNEX --------------------------------------->

# Annex 1. Agenda

# Annex 2. List of participants

```{r participants}

# COMPLETE PARTICIPANTS LIST ##################################################

# Table caption
set.caption('**Table X:** Participants list.')

# Output table
pander(style_table0(part_tab), missing = "-")

```


# Annex 3. Additional results

## Results all readers

**Data Overview**

```{r tab1_sum_stat}

# DATA SUMMARY STATISTICS - All readers #######################################

# Table caption
set.caption('**Table X:** Summary of statistics; PA (%), CV (%) and APE (%).')

# Output table
pander(style_table0(sum_stat), missing="")

```

```{r data_overview_all}

# DATA OVERVIEW - All readers #################################################

# Table caption
set.caption('**Table X:** Data overview including modal 
             age and statistics per sample.')

# Output table
pander(style_table0(table1_data), missing="-", style = "simple")

```

```{r num_age_readings}

# NUMBER OF AGE READINGS - All readers ########################################

# Table caption
set.caption('**Table X:** Number of age readings table gives an overview of 
             number of readings per reader and modal age. The total numbers of 
             readings per reader and per modal age are summarized at the end 
             of the table.')
# Output table
pander(style_table2(num_read_comp),missing="-")

```

```{r ac}

# AGE COMPOSITION - All readers ###############################################

# Table caption
set.caption('**Table X:** Age composition by reader gives a 
             summary of number of readings per reader.')

# Output table
pander(style_table2(ac_tab), missing = "0")

```

```{r mla}

# MEAN LENGTH AT AGE - All readers ############################################

# Table caption
set.caption('**Table X:** Mean length at age per reader is calculated per 
             reader and age (not modal age) and for all readers combined per 
             age. A weighted mean is also given.')

# Output table
panderOptions('round', 1)
panderOptions('keep.trailing.zeros', TRUE)
pander(style_table2(mla_tab), missing = "-")

```

```{r bias_plots, fig.width = 3.5, fig.height = 3, fig.cap = cap_in}

# INDIVIDUAL BIAS PLOTS - All readers #########################################

# Figure caption
cap_in <- '**Figure X:** Bias plots per reader. The mean age recorded 
           +/- 2stdevof each age reader and all readers combined are plotted
           against the modal age. The estimated mean age corresponds to modal 
           age, if the estimated mean age is on the 1:1 equilibrium line 
           (solid line). Relative bias is the age difference between 
           estimated mean age and modal age.'

# Output figure
plot_bias(ad_long, max_age, max_modal)

```

```{r stat_plot, fig.width = 7, fig.height = 4, fig.cap = cap_in}

# PLOT STATISTICS, STDEV, CV AND PA - All readers #############################

# Figure caption
cap_in <- '**Figure X:** CV, PA and (STDEV (standard deviation) are 
           plotted against modal age'

# The coefficient of variation (CV%), percent agreement and 
# the standard deviation (STDEV) are plotted against MODAL age

# Output figure
plot_stat(std_all, pa_all, cv_all)

```

```{r a_dist_plot, fig.width = 7, fig.height = 4, fig.cap = cap_in}

# PLOT AGE DISTRIBUTION - All readers #########################################

# Figure caption
cap_in <- '**Figure X:** The distribution of the age reading errors in 
           percentage by modal age as observed from the whole group of age 
           readers in an age reading comparison to modal age. The achieved 
           precision in age reading by MODAL age group is shown by the spread 
           of the age readings errors. There appears to be no relative bias, 
           if the age reading errors are normally distributed. The 
           distributions are skewed, if relative bias occurs.'

# Output figure
plot_rdist(dif_tab, unique(ad_long$modal_age))

```

```{r rb_plot, fig.width = 7, fig.height = 4, fig.cap = cap_in}

# RELATIEV BIAS - All readers #################################################

# Figure caption
cap_in <- '**Figure X:** The relative bias by modal age as estimated 
           by all age readers combined.'

# Output figure
plot_rb_ma(rb_all)

```

```{r mla_plot, fig.width = 7, fig.height = 4, fig.cap = cap_in}

# PLOT AGE DISTRIBUTION - All readers #########################################

# Figure caption
cap_in <- "**Figure X:** The mean length at age as 
           estimated by each age reader."

# Output figure
plot_mla(mla_num)

```


## Results Advanced readers

**All samples included** 

**Data Overview**

```{r tab1_sum_stat_ex}

# DATA SUMMARY STATISTICS - Advanced readers ##################################

# Figure caption
set.caption('**Table X:** Summary of statistics; PA (%), CV (%) and APE (%) 
             based on advanced readers only.') 

# Output figure
pander(style_table0(sum_stat_ex), missing="")

```

```{r data_overview_exp}

# DATA OVERVIEW - Advanced readers ############################################

# Table caption
set.caption('**Table X:** Data overview including modal age and statistics
             per sample for advanced readerws only.') 

# Output table
pander(style_table0(table1_data_ex), missing = "-", style = "simple")


```

```{r num_age_readings_ex}

# NUMEBR OF AGE READINGS - Advanced readers ###################################

# Table caption
set.caption('**Table X:** Number of age readings table gives an overview of 
             numberof age readings per advanced reader and modal age. The total 
             numbers of readings per reader and per modal age are summarized 
             at the end of the table.')

# Output table
pander(style_table2(num_read_comp_ex),missing="-")

```

```{r ac_ex}

# AGE COMPOSITION - Advanced readers ##########################################

# Table caption
set.caption('**Table X:** Age composition by advanced reader.')

# Output table
pander(style_table2(ac_tab_ex), missing = "0")

```

```{r mla_ex}

# MEAN LENGTH AT AGE - Advanced readers #######################################

# Table caption
set.caption('**Table X:** Mean length at age by advanced reader.')

# Output table
panderOptions('round', 1)
panderOptions('keep.trailing.zeros', TRUE)
pander(style_table2(mla_tab_ex), missing = "-")


```

```{r bias_table_ex}

# Table caption
set.caption('**Table X:** Inter reader bias test for advanced readers.')

# Output table
pander(style_table3(bias_tab_ex), missing = ".", style = "simple")

```

<!-- Plots -->

```{r bias_plots_ex, fig.width = 3.5, fig.height = 3, fig.cap = cap_in}

# Figure caption
cap_in <- "**Figure X:** Bias plot for advanced readers"

# Output figure
plot_bias(ad_long_ex, max_age_ex, max_modal_ex)

```

```{r stat_plot_ex, fig.width = 7, fig.height = 4, fig.cap = cap_in}

# Figure caption
cap_in <- '**Figure X:** CV, PA and (STDEV (standard deviation) 
           are plotted against modal age'


# Output figure
plot_stat(std_all_ex, pa_all_ex, cv_all_ex)

```

```{r a_dist_plot_ex, fig.width = 7, fig.height = 4, fig.cap = cap_in}

# Figure caption
cap_in <- '**Figure X:** The distribution of the age reading errors in percentage
           by modal age as observed from the advanced age readers in an age
           reading comparison to modal age. The achieved precision in age 
           reading by modal age group is shown by the spread of the age 
           readings errors. There appears to be no relative bias, if the age
           reading errors are normally distributed. The distributions are 
           skewed, if relative bias occurs.'

# Figure output
plot_rdist(dif_tab_ex,unique(ad_long_ex$modal_age))

```

```{r rb_plot_ex, fig.width = 7, fig.height = 4, fig.cap=cap_in}

# Figure caption
cap_in <- '**Figure X:** The relative bias by modal age as 
           estimated by all age readers combined.'

# Output figure
plot_rb_ma(rb_all_ex)

```

```{r mla_plot_ex, fig.width = 7, fig.height = 4, fig.cap = cap_in}

# Figure caption
cap_in <- '**Figure X:** The mean length at age as estimated by each age reader
           only including advanced readers.'

# Output figure
plot_mla(mla_num_ex)

```


# Annex 4. ToRs for next meeting

# Annex 5. Recommendations

# Annex 6. Report specific annexes
